Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-08-20 paper/main.tex
add (preliminary) PDFs of surface maps
move Supplementals to separate file

\documentclass[english,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage{babel}
\usepackage[section]{placeins}
\usepackage{flafter}
\usepackage{comment}
\usepackage{breakurl}
\usepackage{svg}
\usepackage[labelfont=bf,font=small]{caption}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm,includeheadfoot]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
%\setlength{\headheight}{40pt}
%\lhead{\textsc{\scidatalogo}}
\usepackage[comma,super,sort&compress]{natbib}

% \usepackage{helvet}

@@

% brain mapping via fMRI
Studies in the field of neuropsychology and neuroimaging
(\citep[e.g.,][]{penfield1950cerebral, fox1984noninvasive}) have shown that
different parts of the brain are specialized for different perceptual and
cognitive functions.
% occipital cortex for vision -> two pathways
the occipital cortex is considered to be primarily involved in the early stages
of visual perception and giving rise to two distinct [but interacting] pathways
that serve different functions:
% dorsal vs ventral pathway
a) a dorsal stream (the ``how pathway'') that [leads into the parietal lobe,]
and supports [nonconscious] visual guidance of action, and
b) a ventral stream (the ``what pathway'') that [leads into the temporal lobe
and] supports [conscious] perception and recognition.
\citep{goodale1992separate, milner2017two, mishkin1982contribution}.

\todo[inline]{reviewer #1: its clear that where (spatial processing) must take
place in both streams. You should probably acknowledge that.}
% PPA
A classic example of a higher-level visual area in the ventral pathway is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity is observed in the PPA when participants view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
faces or tools) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) (\citep[see reviews][]{epstein2014neural,
aminoff2013role}).
% \citep{aguirre1998area, epstein2014neural, epstein1998ppa, troiani2012object}.

@@

% open question
In this study, we investigate whether increased hemodynamic activity in the PPA
that is usually detected by contrasting blocks of pictures is also present under
more natural conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both
\textit{visual and auditory} spatial information using two naturalistic stimuli
(\citep[see reviews][]{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic}).
% AV stimulus
The current operationalization of visual spatial perception is based on an
annotation of cuts and depicted locations in the audio-visual movie ``Forrest
Gump'' \citep{haeusler2016cutanno}, while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech occurring in the movie's audio-description
\citep{haeusler2021studyforrest}.
% pictures -> movie -> audio-description
The movie stimulus shares the stimulation in the visual domain with classical
localizer stimuli, while featuring real-life-like visual complexity and
naturalistic auditory stimulation. The audio-description maintains the
naturalistic nature of the movie stimulus, but limited to the auditory domain.
% current GLM contrasts
We applied model-based, mass-univariate analyses to BOLD fMRI data from both
naturalistic stimuli \citep{hanke2016simultaneous, hanke2014audiomovie},
available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}.
% comparison to previous GLM
We compare current results to results from a previously performed model-based,
mass-univariate analysis that was applied to data from a conventional
block-designed functional localizer paradigm that was performed with the same
set of participants \citep{sengupta2016extension}.
% intro to hypo a
Similarly to the functional localizer, we currently also capitalize on events
that should evoke the cognitive processing of spatial information.
% hypo a
Thus, we hypothesized that our whole-brain analyses would reveal increased
hemodynamic activity in medial temporal regions that were defined functionally
defined as the PPA by the previous analysis of the data from the block-designed
localizer \citep{sengupta2016extension}.
%hypo b: individuals
We hypothesized further that an purely auditory stimulus could, in principle,
localize the PPA as an example of a ``visual area'' in individual persons,
% application in individuals
and may offer an alternative paradigm to assess brain functions in visually
impaired individuals.

% DISABLE RESULTS
%% results: group
%On a group average level,
%% operationalization in naturalistic stimuli
%results demonstrate that our approach to operationalize spatial perception
%during two naturalistic stimuli lead to increased hemodynamic activity in the
m%PPA.
%% anterior vs. posterior
%On both a group and individual participant level, the comparison of results from the
%three datasets also suggests functional differences between the anterior and
%posterior PPA.
%% what does it mean
%The current data add evidence to the hypothesis that the PPA might consist of
%submodules that work together during visual perception of landscapes (cf.
%\citep{baldassano2013differential}).
%%
%Lastly, our results suggest that the PPA's anterior part can be localized in
%individual participants by contrasting high-level semantic information occurring in
%an auditory naturalistic stimulus.

@@

@@

%#11 question
The fact that clusters of responses to the auditory stimulus are spatially restricted to
the anterior part of clusters from both visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual stimuli compared to a purely auditory stimulus.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence
that the PPA can be divided into functionally subregions that might process
different stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, lescroart2019human, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
In contrast, the aPPA responds more to high-level features of scenes (e.g.
real-word size \citep{park2015parametric}; a scene's abstract category
\citep{marchette2015outside, watson2016patterns}) and objects (e.g. spatial
contextual associations \citep{aminoff2007parahippocampal, aminoff2013role})
than the pPPA.
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA exhibits more coactivation with the occipital visual cortex than the
aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus
% (TOS) anterior
Activity in the aPPA, on the other hand, is found to be correlated with
components of the default mode network, including caudal inferior parietal lobe,
retrosplenial complex, medial prefrontal cortex, and lateral surface of
the anterior temporal lobe \citep{baldassano2013differential,
baldassano2016two}.
% conclusion: subregions
\citet{baldassano2013differential} proposes that the PPA creates a complete
scene representation, based on different aspects of a visual scene processed in
subregions of the PPA.
% Their distinct connectivity properties do suggest that each may be involved
% in specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual
% features like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects inherent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as
inherent in both visual and verbal stimuli.

@@

@@

% AV design matrix
The design matrix for the first-level time-series GLM analysis of the movie
comprised regressors for the 12 event categories of the movie listed in
Table~\ref{tab:events}.
% AD design matrix
Similarly, the design matrix for the analysis of the audio-description comprised
regressors for the 13 event categories of the audio-description, also listed in
Table~\ref{tab:events}.
% AD regressors in AV
In order to implement cross-modal control contrasts, the design matrix for the
movie stimulus also contained the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
Likewise, the design matrix for the audio-description included the five movie
cut related regressors (\texttt{vse\_new}, \texttt{vse\_old}, \texttt{vlo\_ch},
\texttt{vp\_new}, \texttt{vpe\_old}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of \texttt{vpe\_old}
in segment 3; see Table~\ref{tab:events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to
compensate for regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant- and run-specific motion estimates (translation and
rotation) were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter
(cutoff period of \unit[150]{s}) as the BOLD time series.

@@

\section*{Data availability}

@@

\section*{Code availability}

@@

\section*{Competing financial interests}

@@

\appendix

\setcounter{figure}{0}
\makeatletter
\renewcommand{\thefigure}{S\@arabic\c@figure}
\makeatother

\section{Supplementary Materials}

\subsection*{Robustness of main findings across alternative contrasts}

In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
audio-description (see Table~\ref{tab:contrasts}).
% how
Contrasts differ in contrasted categories based on ``how well'' averaged events
within categories were considered to represent spatial and non-spatial
information, and the number of events in the stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
group-template (MNI152 space) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

% AV PPA contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
% intracalcarine, cuneal, ling.c
% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.

% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
% temporal occipital fusiform cortex
Reliably across all five movie contrasts, we find bilaterally significant
clusters that overlap with the PPA group overlap
(see Figure~\ref{fig:stability-slices}).
% AV: RSC & LOC
Several contrasts of the movie also yielded bilaterally significant clusters in
the ventral precuneal cortex and posterior cingulate gyrus (i.e. retrosplenial
complex; contrasts 1, 4, 5), and lateral occipital cortex (contrasts 1, 2, 4,
5).

% AD PPA contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r)
% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
% 4 PPA (l/r); RSC (l/r), LOC (l/r)
% 5 PPA (l/r); RSC (l/r), LOC (-/-)
% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C.; left frontal pole
% 8 PPA (-/-); RSC (-/-), LOC (-/-)

% AD: results
In results from the analysis of the audio-description, all contrasts except
contrast 7 and 8  yielded significant bilateral clusters in anterior regions of
the group PPA overlap (see Figure~\ref{fig:stability-slices}).
% AD: RSC & LOC
Contrasts of the audio-description also yielded bilaterally significant clusters
in the ventral precuneus (all contrasts except contrasts 8) and lateral
occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
7).
% concluding stament regarding PPA, RSC, and LOC
Results across contrasts of both naturalistic stimuli indicate that our findings
regarding the PPA but also RSC and LOC are robust and do not depend on the
design of one specific contrasts.
% but:
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 7 and 8 (\texttt{se\_new}, \texttt{se\_old} > non-spatial
categories, and \texttt{se\_new} > non-spatial categories) that used the most
heterogeneous categories (nouns indicating switches to other settings) and a low
amount of events yielded neither a significant cluster in the right-hemispheric
nor left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

\subsection*{Incidental results}

Several contrasts yielded significant clusters in superior temporal cortices
(bilateral in contrasts 3, 6, 7; unilateral right in contrast 2).
% AD: auditory cortices
Further, contrasts that compare, possibly among others, nouns indicating a
switch to another setting (categories \texttt{se\_new} or \texttt{se\_old}) to
non-spatial categories yielded significant clusters in superior temporal
cortices (bilateral: contrasts 3, 6, 7; unilateral right: contrast 2).
% interpretation 1
This suggests that variance correlating with lower level auditory processes was
not averaged out across events (e.g. switches to another setting might often not
just cued by the narrator but also by a change of the soundscape or cued by a
the start of a new song) and the employed nuisance regressors did not capture
this variance appropriately.
% interpretation 2
Another possibility might be that increased hemodynamic activity in superior
temporal cortices reflect a bias towards lower-level auditory perceptual
processes on the positive side of the GLM contrasts.
% soundscape
Increased activity in primary and secondary auditory cortices could be
attributed to changes in the soundscape that possibly accompany the narrator
when he is indicating the switch to another setting by describing its identity
or layout.

Lastly, contrasts of the audio-description stimulus yielded clusters
in regions that were classified as statistically significant in two or less contrasts.
% contrast 2
In detail, contrast 2 yielded clusters in the anterior cingulate gyrus
(bilateral), right frontal pole, right frontal medial cortex, and right putamen.
% contrast 3
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
% contrast 6
Contrast 6 shows one additional cluster in the right medial frontal cortex.
% contrast 7
Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
left insular.
% concluding statement
Here again, significantly increased activation beyond areas known to be involved
in processing of spatial information could be attributed to stimulus features of
the naturalistic stimulus that were not sufficiently controlled leading to a
bias in the contrasts.

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster corrected)
        across all contrasts for both naturalistic stimuli.
        The audio-description's contrasts 1-8 (blue)
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:contrasts}).
        Cluster are overlaid on top of the MNI152 T1-weighted head template
        with the acquisition field-of-view for the audio-description study
        highlighted.
        Black: outline of the union of individual PPA ROIs reported by \citet{sengupta2016extension}.
        }
    \label{fig:stability-slices}
\end{figure*}

\subsection*{Control contrasts}

% ---------- AV control contrasts ----------
% 6: nothing; 7 nothing; 8: nothing; 9: nothing; 10 se_new > se_old (nouns but
% in AV stimulus): LOC (l/r) right PPA, bilateral, sup. lat. occ. c., sup.
% parietal lobe (right)

% ---------- AD control contrasts ----------
% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
%10 PPA (-/-); RSC (-/-), LOC (-/-)
%11 PPA (-/-); RSC (-/-), LOC (-/-),
%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
%13 PPA (-/-); RSC (-/-), LOC (-/-)

% intro
For each naturalistic stimulus, we created several control contrasts.
% movie contrasts: not cut condition vs. cuts
To test for the specificity of the main findings within the movie fMRI data, we
created four contrasts that compared hemodynamic activity during frames within
movie shots (\texttt{no\_cut} category) with movie cut related categories (see
Table~\ref{tab:contrasts}).
% results
None of these four contrasts yielded a significant cluster, suggesting that the
observed differential hemodynamic response in the PPA for events defined by
particular movie cuts is not observed for other arbitrarily selected time point
in the movie.

% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
% \texttt{vse\_old}.
The correlation of regressors across stimuli (Figure~\ref{fig:reg-corr}) showed
a moderate correlation among cuts to a setting depicted for the first time
(movie \texttt{vse\_new}) and nouns indicating a switch to a setting occurring
for the first time (audio-description \texttt{se\_new}), and cuts to a
recurringly depicted setting (movie {\texttt{vse\_old}) and nouns indicating a
switch a recurring setting (audio-description \texttt{se\_old}).
%
Hence, we computed an indentical contrast ({\texttt{se\_new} >
\texttt{se\_old}), comparing the audio-description's voice-over narrator nouns
for the movie data and the audio-description.
% results
While for the movie data the contrast yielded a significant cluster in the right
PPA, not in its anterior portion, and bilateral clusters in the superior lateral
occipital cortices (the right hemispheric cluster extending into the superior
parietal cortex), not significant differences where found for the
audio-description (unthresholded contrast maps are available on NeuroVault).
%
These results suggest that in the absence of the actual visual stimulation, the
narrator's description of scene properties correlated with setting changes did
not co-occur with increased hemodynamic activity in areas associated with the
processing of spatial information.

% AD stimulus
Finally for the analysis of the audio-description, we computed control contrasts
based on events of the annotated movie cuts (Table~\ref{tab:contrasts}) in order
to evaluate the influence of stimulus features correlated with these visual
events that remain present in the audio-description, such as changes in the
soundscape.
% results
Two of five contrasts yielded significant clusters.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.
%
The absence of observable hemodynamic response differences in the PPA suggests
that without the visual information in the movie stimulus, no, or substantially
less, processing of stimulus content with respect to spatial information
co-occurred with the timing of the movie cuts.

\subsection*{Surface maps}

\todo[inline]{Just mention this part in the main document via 'the corresponding
surface plots (Fig xy) can be found in the supplemental materials'?}
\todo[inline]{write intro regarding purpose of additional surface plots?}

% reconstruction MNI
Cortical reconstruction of the MNI152 T1-weighted brain template
[MNI152\_T1\_1mmi\_brain.nii.gz] was performed using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
\citep{dale1999cortical}.
% reconstruction: individual results
Subject-specific cortical surfaces are part of pre-existing
\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
that used FreeSurfer v5.3.0 to reconstruct surfaces from T1-weighted images and
an additional high-resolution T2-weighted image.

% projection
Results were projected onto the corticals surface using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
'mri\_vol2surf' command.
% smoothing
Group and individual PPAs were additionally patially smoothed applying a
Gaussian kernel with full width at half maximum (FWHM) of \unit[3.0]{mm}.

\subsubsection*{Group results}
Group results see Table~\ref{tab:res-ao-group1} for AO results,
Table~\ref{tab:res-av-group1} for AV results, and
Figure~\ref{fig:grp_ao_av_c1_surf} for surface maps.

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}

    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
      cluster-corrected) of activity correlated with the processing of spatial
      information are projected onto the surface of the MNI152
      T1-weighted template.
      %
      The results of the audio-description's primary $t$-contrast (blue) that
      compares geometry-related nouns spoken by the narrator to non-spatial
      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
      on the movie's primary $t$-contrast (red) that compares cuts to a
      setting depicted for the first time with cuts within a recurring setting
      (\texttt{vse\_new > vpe\_old}).
      %
      Black: outline of the union of individual PPA ROIs reported by
      \citet{sengupta2016extension}.
    }
    \label{fig:grp_ao_av_c1_surf}
\end{figure*}

\subsubsection*{Stability}
Group results see Figure~\ref{fig:grp_ao_av_stability} for surface maps.

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
        corrected) across all contrasts for both naturalistic stimuli.
        The audio-description's contrasts 1-8 (blue)
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:contrasts}).
        Cluster are projected onto the surface of the
        MNI152 T1-weighted template.
        Black: outline of the union of individual PPA ROIs reported by
        \citet{sengupta2016extension}.
        }
    \label{fig:grp_ao_av_stability}
\end{figure*}

\subsubsection*{Individual resultsStability}

Individual results see Figure~\ref{fig:subjs_ao_av_c1_surf} for surface maps.
\todo[inline]{RSC in of AV is essentially not visible}

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/subjs_ao_av_c1_surf}
    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
        cluster-corrected)
        projected onto subject-specific brain surface that were
        [re]constructed from individual T1-weighted brain images.
        The results of the audio-description's primary
        $t$-contrast (blue) that compares geometry related nouns to non-
        geometry related nouns spoken by the narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (red) that compares cuts to setting depicted for
        the first time with cuts within a recurring setting
        (\texttt{vse\_new > vpe\_old}).
        Black: outline of participant-specific PPA ROIs reported by
        \citet{sengupta2016extension}.
        }
    \label{fig:subjs_ao_av_c1_surf}
\end{figure*}

>>>>

\documentclass[english,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage{babel}
\usepackage[section]{placeins}
\usepackage{flafter}
\usepackage{comment}
\usepackage{breakurl}
\usepackage{svg}
\usepackage[labelfont=bf,font=small]{caption}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm,includeheadfoot]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
%\setlength{\headheight}{40pt}
%\lhead{\textsc{\scidatalogo}}
\usepackage[comma,super,sort&compress]{natbib}
\usepackage{xr}
\externaldocument{suppl}
% \usepackage{helvet}

@@

\todo[inline]{possibly drop some words in ``how''-``what'' sentence if it's
considered to be wordy}

% brain mapping via fMRI
Studies in the field of neuropsychology and neuroimaging
(\citep[e.g.,][]{penfield1950cerebral, fox1984noninvasive}) have shown that
different parts of the brain are specialized for different perceptual and
cognitive functions.
% occipital cortex for vision -> two pathways
the occipital cortex is considered to be primarily involved in the early stages
of visual perception and giving rise to two distinct [but interacting] pathways
that serve different functions:
% dorsal vs ventral pathway
a) a dorsal stream (the ``how pathway'') that [leads into the parietal lobe,]
and supports [nonconscious] visual guidance of action, and
b) a ventral stream (the ``what pathway'') that [leads into the temporal lobe
and] supports [conscious] perception and recognition.
\citep{goodale1992separate, milner2017two, mishkin1982contribution}.
% PPA
A classic example of a higher-level visual area in the ventral pathway is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity is observed in the PPA when participants view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
faces or tools) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) (\citep[see reviews][]{epstein2014neural,
aminoff2013role}).
% \citep{aguirre1998area, epstein2014neural, epstein1998ppa, troiani2012object}.

@@

% open question
\todo[inline]{I revised the following paragraph; I guess it's okay that way}
In this study, we investigate whether increased hemodynamic activity in the PPA
that is usually detected by contrasting blocks of pictures is also present under
more natural conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both
\textit{visual and auditory} spatial information using two naturalistic stimuli
(\citep[see reviews][]{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic}).
% AV stimulus
The current operationalization of visual spatial perception is based on an
annotation of cuts and depicted locations in the audio-visual movie ``Forrest
Gump'' \citep{haeusler2016cutanno}, while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech occurring in the movie's audio-description
\citep{haeusler2021studyforrest}.
% pictures -> movie -> audio-description
The movie stimulus shares the stimulation in the visual domain with classical
localizer stimuli, while featuring real-life-like visual complexity and
naturalistic auditory stimulation. The audio-description maintains the
naturalistic nature of the movie stimulus, but limited to the auditory domain.
% current GLM contrasts
We applied model-based, mass-univariate analyses to BOLD fMRI data from both
naturalistic stimuli \citep{hanke2016simultaneous, hanke2014audiomovie},
available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}.
% comparison to previous GLM
We compare current results to results from a previously performed model-based,
mass-univariate analysis that was applied to data from a conventional
block-designed functional localizer paradigm that was performed with the same
set of participants \citep{sengupta2016extension}.
% intro to hypo a
Similarly to the functional localizer, we currently also capitalize on events
that should evoke the cognitive processing of spatial information.
% hypo a
Thus, we hypothesized that our whole-brain analyses would reveal increased
hemodynamic activity in medial temporal regions that were defined functionally
defined as the PPA by the previous analysis of the data from the block-designed
localizer \citep{sengupta2016extension}.
%hypo b: individuals
We hypothesized further that an purely auditory stimulus could, in principle,
localize the PPA as an example of a ``visual area'' in individual persons,
% application in individuals
and may offer an alternative paradigm to assess brain functions in visually
impaired individuals.

% DISABLE RESULTS
%% results: group
%On a group average level,
%% operationalization in naturalistic stimuli
%results demonstrate that our approach to operationalize spatial perception
%during two naturalistic stimuli lead to increased hemodynamic activity in the
%PPA.
%% anterior vs. posterior
%On both a group and individual participant level, the comparison of results from the
%three datasets also suggests functional differences between the anterior and
%posterior PPA.
%% what does it mean
%The current data add evidence to the hypothesis that the PPA might consist of
%submodules that work together during visual perception of landscapes (cf.
%\citep{baldassano2013differential}).
%%
%Lastly, our results suggest that the PPA's anterior part can be localized in
%individual participants by contrasting high-level semantic information occurring in
%an auditory naturalistic stimulus.

@@

\todo[inline]{Summarize some methods here?}

@@

%#11 question
The fact that clusters of responses to the auditory stimulus are spatially
restricted to the anterior part of clusters from both visual paradigms raises
the question if the revealed correlation patterns can be attributed to different
features inherent in the visual stimuli compared to a purely auditory stimulus.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, lescroart2019human, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
In contrast, the aPPA responds more to high-level features of scenes (e.g.
real-word size \citep{park2015parametric}; a scene's abstract category
\citep{marchette2015outside, watson2016patterns}) and objects (e.g. spatial
contextual associations \citep{aminoff2007parahippocampal, aminoff2013role})
than the pPPA.
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA exhibits more coactivation with the occipital visual cortex than the
aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
Activity in the aPPA, on the other hand, is found to be correlated with
components of the default mode network, including caudal inferior parietal lobe,
retrosplenial complex, medial prefrontal cortex, and lateral surface of the
anterior temporal lobe \citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
\citet{baldassano2013differential} proposes that the PPA creates a complete
scene representation, based on different aspects of a visual scene processed in
subregions of the PPA.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
spatial features that are intrinsic to pictures or movie shots of
landscapes.
% aPPA
The aPPA might be more concerned with non-visual spatial features
(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) that
are intrinsic to visual but also verbal stimuli.

@@

\todo[inline]{Maybe add sentence here that ``further studies are obvious''}

@@

% AV design matrix
The design matrix for the first-level time-series GLM analysis of the movie
comprised regressors for the 12 event categories of the movie listed in
Table~\ref{tab:events}.
% AD design matrix
Similarly, the design matrix for the analysis of the audio-description comprised
regressors for the 13 event categories of the audio-description, also listed in
Table~\ref{tab:events}.
% AD regressors in AV
In order to implement cross-modal control contrasts, the design matrix for the
movie stimulus also contained the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
Likewise, the design matrix for the audio-description included the five movie
cut related regressors (\texttt{vse\_new}, \texttt{vse\_old}, \texttt{vlo\_ch},
\texttt{vp\_new}, \texttt{vpe\_old}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of \texttt{vpe\_old}
in segment 3; see Table~\ref{tab:events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to
compensate for regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant-specific and run-specific motion estimates (translation
and rotation) were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter
(cutoff period of \unit[150]{s}) as the BOLD time series.

@@

\section*{Data Availability}

@@

\section*{Code Availability}

@@

\section*{Competing Interests}

@@
